---
title: "Data analysis on marriage licences in Toronto"
subtitle: 
author: "Renjing Liu"
thanks: "Code and data are available at: https://github.com/MaxLiu728/First_Paper.git"
date: "2021/1/28"
output: html_document
abstract:
output: ###
toc: ###
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(readr)
library(dplyr)
```

# Introduction



# Data
```{r}
raw_data <- readr::read_csv("D:/MI/2178/Paper1/First_Paper/inputs/raw_data.csv")
```

```{r}
# Explore how many marriage licences issued by each civic centre on average among the 10 years.
Df1<- raw_data %>%
  group_by(CIVIC_CENTRE) %>%
  summarise(mean_value= round(mean(MARRIAGE_LICENSES)))
Df1<- knitr::kable(Df1, format='simple')
Df1



# Explore how many marriage licences issued by each civic centre on average in each year
Df2<- raw_data %>%
  group_by(CIVIC_CENTRE, year) %>%
  summarise(mean_value= round(mean(MARRIAGE_LICENSES)))
Df2<- knitr::kable(Df2, format='simple')
Df2
```

```{r}
#Explore the popular months people choose to get marriage licences
Df_Month<- raw_data %>%
  group_by(CIVIC_CENTRE, month) %>%
  summarise(Avg_licences= round(mean(MARRIAGE_LICENSES)))
  
# Create table for visualization

Df2_1<- raw_data %>%
  group_by(CIVIC_CENTRE, year) %>%
  summarise(mean_value= round(mean(MARRIAGE_LICENSES)))


p1<- ggplot(data= as.data.frame(Df2_1))+geom_line(aes(x= year, y= mean_value, color= CIVIC_CENTRE))

p2<- ggplot(data= as.data.frame(Df_Month))+geom_point(aes(x=month, y= Avg_licences, color=CIVIC_CENTRE))


```

```{r}
dput(raw_data)
```


# Model

# Results


# Discussion



## First discussion point
People prefer to get married in summer.

## Second discussion point
The issued marriage licences did differ cross the type of civic centre; 
TO was the most popular civic centre before 2018, but the number of issued marriage licences experienced a dramartic decrease after that, more people begun to choose  NY and SC
## Weakness and next steps
I am curious the what factors affect people's choice on civic centre, like distance/ area/... 
I am also curious about why people prefer to get married in summer, I plan to have one-to-one talk with several people, to get more insights.


# Appendix {-}


# References

